### 2018-03-05 Paper/jaccardbaetica.tex
modify material and method

All the amphora stamps belong to Dressel 20 types \citep{martin-kilcher_romischen_1994}. Dressel 20 is commonly associated with transportation of Baetican olive oil through the provinces during the Roman Empire \citep{berni_millet_epigrafianforica_2008}. Most Dressel 20 were marked in stamps and \textit{tituli picti} and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used for almost three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body.

The information of the stamps is known as \textit{tria nomina} (HABLAR SOBRE EL DEBATE DE LOS INDIVIDUOS DE ACEITE O YO QUE SE). \textit{Tria Nomina} was mostly formed for a code three of letters. These letters can appear in a abbreviated form or complete \citep{berni_millet_amphora_1996}

@@

Our case study examines the relation between the distribution of amphoric stamps and the workshops. We studied a dataset of 3787 stamps collected from CEIPAC database (CITAR). However, the 70 \% of stamps cannot be tested due to fragmentation or imcomplete information. Consequently, we discard integrate the fragmented stamps in our dataset.

We finally filter a total sample of 990 stamps composed by 131 different stamps from 81 workshops. The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance.

The chronology in the workshops is widely diverse from I-III B.C. However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason can be that most of them were partially excavated and only focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

It could be due to several reason. On the one hand, the use of this amphoric stamps were exclusively running by the owner or family to distinguish the amphora workshop (CITAR). On the other, it could be somehow a batch sistematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases.

>>>>

All the amphora stamps belong to Dressel 20 types \citep{dressel,martin-kilcher_romischen_1994}. Dressel 20 is commonly associated with transportation of Baetican olive oil through the provinces during the Roman Empire \citep{berni_millet_epigrafianforica_2008}. Most Dressel 20 were marked in stamps and \textit{tituli picti} and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used for almost three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body.

The information of the stamps is shown in different forms and letter content and it seems that there was not a unique criteria (CITAR). Stamps was mostly formed for a code of three letters. There letters can appear in a abbreviated form or complete and they are known as \textit{Tria Nomina} \citep{berni_millet_amphora_1996}.

@@

Our case study examines the relation between the distribution of amphoric stamps and the workshops. We studied a dataset of 3787 stamps collected from different amphora workshops in Baetica provice (see CEIPAC database). The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance.

However, the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 990 stamps composed by 131 different stamps from 81 workshops.

The chronology in the workshops is widely diverse from the first to the third centuries AD . However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason may be that most of them were partially excavated and only focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

It could be due to several reason. On the one hand, the use of this amphoric stamps were exclusively running by the owner or family to distinguish the amphora workshop (CITAR). On the other, it could be somehow a batch systematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases.
